Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-11-11 doc/paper.Rmd
results for profiles

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

@@

@@

The idea therefore is to first use these raw values of the profile directly in the chumbley algorithm, and see how the algorithm performs for different coarseness values (smoothing parameter as referred in the function LOWESS used in the chumbley algorithm)

>>>>

errorratecoarse <- function(data, alpha) {
  summ <- data %>% filter(!is.na(p_value)) %>%
    mutate(signif = p_value < alpha) %>%
    group_by(wv, wo, coarse, match, signif) %>% tally()
  summ$error <- with(summ, match != signif)
  summ$alpha <- alpha

  rates <- summ %>% group_by(wv, wo, coarse, match, alpha) %>% summarize(
    rate = n[error==TRUE]/sum(n)
  )
  rates %>% spread(match,rate) %>% rename(
    actual = `FALSE`,
    beta = `TRUE`
  )
}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

@@

errors2 <- rbind(errorratecoarse(all, 0.001), 
                errorratecoarse(all, 0.005), 
                errorratecoarse(all, 0.01), 
                errorratecoarse(all, 0.05))
```

```{r data-profiles}
if (!file.exists("../data/all-profiles.rds")) {
  files <- dir("../data/profiles/", pattern="csv")
  all <- data.frame()
  for (file in files) {
    tmp <- read.csv(file=file.path(path="../data/profiles", file)) 
    #print(names(tmp))
    if (length(grep("coarse",names(tmp))) == 0)
      tmp$coarse <- gsub(".*coar-(.*).csv", "\\1", file)
    if (length(grep("x",names(tmp)) > 0)) tmp <- tmp %>% select(-x)
    all <- rbind(all, tmp)
  }
  all <- all %>% filter(land1_id < land2_id)
  all <- all %>% mutate(coarse = as.numeric(gsub("pt", ".", coarse)))
  saveRDS(all, file="../data/all-profiles.rds")
} else {
  all <- readRDS("../data/all-profiles.rds")
}

@@

\hh{XXX ideas should go to the previous section on setting up the study; in this section we focus on results only XXX}
The idea therefore is to first use these raw values of the profile directly in the chumbley algorithm, and see how the algorithm performs for different coarseness values (smoothing parameter as referred in the function LOWESS used in the chumbley algorithm)

```{r, fig.cap="Type II errors for different levels of coarseness. XXX We need more values around .25"}
errors2 %>% ggplot(aes(x = coarse, y=beta, colour=factor(alpha))) +
  geom_point() + geom_line() +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2")
```
